% \documentclass[a4paper,12pt]{article}
% \usepackage{TLCresume}
% \begin{document}


\vspace*{12pt}
\subsection{{Associate Researcher }\hfill July 2022 - Current}
\subtext{Smart Information Flow Technologies (SIFT) \hfill Lexington, MA}
\begin{zitemize}
    \item Research and develop state-of-the-art cybersecurity technologies for critical government problem solutions.
    \item Leverage open-source systems, virtualization, and various programming techniques to build a strong PoC. 
    \item Adapt offensive and defensive security standards from MITRE ATT\&CK and NIST frameworks.
\end{zitemize}

\vspace*{15pt}
\subsection{{Graduate Researcher }\hfill April 2021 - May 2022}
\subtext{University of South Carolina \hfill Columbia, SC}
\begin{zitemize}
    \item Developed and maintained front-end and back-end ArcGIS web application solutions for South Carolina DoT. 
    \item Utilize JavaScript, HTML, CSS, Dojo.js, Angular.js and Node to build original ArcGIS widgets and plugins.
    \item Use GitHub and ArcGIS Web Builder to deploy new features and present to clients. 
\end{zitemize}

% \vspace*{6pt}
% \subsection{{Resident Mentor }\hfill August 2018 - May 2021}
% \subtext{University of South Carolina \hfill Columbia, SC}
% \begin{zitemize}
%     \item Serve as a professional and collegiate life resource to over 20 freshmen students. 
%     \item Host community gatherings, enforce policy, and manage crisis to over 400 freshmen residents. 
%     \item Maintain 24 hour on-call duty for health and safety emergencies. 
% \end{zitemize}

\vspace*{12pt}
\subsection{{Software Engineer in Test Intern }\hfill May 2020 - August 2020}
\subtext{CVS Health \hfill Cumberland, RI}
\begin{zitemize}
    \item Develop JavaScript automation functions for three different mobile, web, and desktop applications.
    \item Leverage Cucumber.js, Karma.js, Chai + Mocha.js, Node and Angular technologies.
    \item Participate in Agile project workflow with weekly scrum meetings and bi-weekly sprints. 
\end{zitemize}

\vspace*{15pt}
\subsection{{IT Support }\hfill April 2019 - March 2020}
\subtext{University of South Carolina \hfill Columbia, SC}
\begin{zitemize}
    \item Build and image computer systems for scientific engineering departments of over 100 faculty and staff.
    \item Utilize common troubleshooting solutions for windows and unix systems as well as printers, routers, and other lab hardware
\end{zitemize}


% \end{document}



